**The status of the microbial census: an update**

### 2015-12-04 results/tables/build_table_1.Rmd
Moved some stuff around

data <- read.table(file="data/process/coverage_by_category_and_time.tsv", header=T)
int_cols <- grepl("count", colnames(data)) | grepl("sobs", colnames(data))
float_cols <- !int_cols

data[,int_cols] <- format(data[,int_cols], big.mark=',')
data[,float_cols] <- format(data[,float_cols], big.mark=',', nsmall=1, digits=1)

data_current <- data[,!(grepl("pre", colnames(data)) | grepl("post", colnames(data)))]

@@

>>>>

data <- read.table(file="data/process/coverage_by_category_and_time.tsv", header=T)
data_current <- data[,!(grepl("pre", colnames(data)) | grepl("post", colnames(data)))]

@@

int_cols <- grepl("count", colnames(composite)) | grepl("sobs", colnames(composite))
float_cols <- !int_cols
float_cols[1:2] <- FALSE

composite[,int_cols] <- format(composite[,int_cols], big.mark=',')
composite[,float_cols] <- format(composite[,float_cols], big.mark=',', nsmall=1, digits=1)
